---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# rxnorm

<!-- badges: start -->
[![Project Status: WIP – Initial development is in progress, but there has not yet been a stable, usable release suitable for the public.](https://www.repostatus.org/badges/latest/wip.svg)](https://www.repostatus.org/#wip)
<!-- badges: end -->

> Access drug name and class using RxCUI from the National Library of Medicine RxNorm RESTful API.

## Scope

`rxnorm` is an R package providing a basic interface to query the National Library of Medicine RxNorm RESTful API using RxCUI. The goal is to provide a simple way to translate RxCUI into drug categories with incremental levels of generality: specific drug names `r knitr::asis_output("\U02192")` brand names `r knitr::asis_output("\U02192")` drug classes.

## Installation

You can install `rxnorm` from [GitHub](https://github.com/) with:

``` r
devtools::install_github("nt-williams/rxnorm")
```

## Example

```{r}
library(rxnorm)
```

Query the API for the RxNorm name:

```{r}
get_rx(1011485)
```

Query the API for the brand name:

```{r}
get_bn(1011485)
```

Query the API for the [WHO ATC](https://www.whocc.no/atc_ddd_index/) drug class:

```{r}
get_atc(1011485)
```

We can further parse ATC codes to varying levels of specificy:

```{r}
get_atc(1011485, "first")
get_atc(1011485, "second")
get_atc(1011485, "third")
get_atc(1011485, "fourth")
```

